---
title: "First Knit"
author: "Cortajha Hunter"
date: "8/19/2019"
output: 
  html_document:
    number_sections: true
    toc: true
---

### `r as.character(Sys.Date())`

```{r include=FALSE,echo=FALSE}
require(tidyverse)
if(!require("imager")) {install.packages("imager");require("imager")}

```

```{r echo=FALSE,out.width='100%'}
xx<-getwd()
Drive_ltr <- strtrim(xx,2)
yy <- str_glue("{Drive_ltr}\\AAA_Owner_Info\\My_photo.jpg")
my_pict <- load.image(yy)
plot(my_pict,axes=FALSE,main="I Figured It Out")
```

# A Little Survey

Here are just a few questions so I can get to know you and so you can get practice submitting an assignment in Canvas.  For each question, insert your answer underneath. Make sure each answer is at the minimum a complete sentence with correctly spelled words and correct puncuation. Half the points in this assignment depend on your picture and name being correct!!  Be sure to put your photo in the AAA_Owner_Info folder and call it My_photo.jpg after first renaming the current one to Koala.jpg . 

##Where are you now?  
What row are you in, front,middle or back?  Do you usually choose a similiar row in other classes? What is the computer number where you are sitting?  How on a scale of 1 to 10 (1=low, 10=high) How you feel about periodic seat re-assignment, say how and why. Teams, have you ever worked on one in a class setting?  

###my answer     
  
   I am sitting at the front of the class. Yes, I am usually at the front because I tend to receive the information better.I am surrently sitting at computer 6. Not sure what periodic seat re-assignment is so my rate would be nutural; a 5. Yes I have worked on a class team. 
     


##Others and You?   
What name do you prefer to be called by your classmates and instructor, if your buddys call you something but you want me to call you something else - what would that be? 

###my answer     
  
   I would prefer to be called by my last name Hunter. 
 




##Aspirations?   
What do you want to achieve in life?  What college subject do you think would be of the greatest interest to you? What degree or certificate are you trying to achieve?

###my answer     
  
   I want to be able to look back and say "I lived my best life, with no regrets". Sociology tends to tug at my attention more than any other subjects. I dont have a limit on my education so i'm going to go all the way to the top; and recieve my doctorate degree. 
 




##Past adventures?  
Have you ever gone to foreign countries, if so which ones, if not Where might you go in the future?  Have you ever been in the military, if so which branch, if not which branch would you choose if you got drafted, and why?

###my answer     
  I ahve yet to go to any foriegn country yet, but I plan to travel everywhere. I will be flying to Belize as my first country. I have never been in the military but if I was to go it would be the Navy beacuse my dad and all my uncles went. 
   
  




##Why are you taking Math 115?  
What grade do you need to attain in stats to not upset your future plans, What is your plan?
 

###my answer     
  
   I need to obtain a C or better in order to transfer, but I have plans on getting an A. 




##Homework Help and Getting around?  
On a scale of 1 to 10, where 1 is a total dummy (doesn't know a mouse from a keyboard) and 10 is a complete geek (knows computer stuff in and out) How do you rate yourself?  Do you have a computer you can use at home? If so, what kind is it (windows, Apple, Linux)? Do you have internet access at home?  
How do you get to class? Are there issues that limit when you can be at the college?Where and when did you attend high school?  Do you currently have a job?

###my answer   
  At this very moment, I honestly rate myself at an 25. My potential is out of this world. I currently do have a computer at home to use which is an Macbook pro. I also have internet acces. I am financing a vehicle and thats how I get back and forth to class. The only problem that would keep me from missing class would be an family emergancy. I attending high school in Los Angeles California at a school called SEA Hyde Park. Finally, I have a job as a care provider.
   
  




